Verification of Stencil Computations with Spatial Specifications

### 2016-08-23 paper.tex
Extend consistency definition to make readOnce optional in the spec
Add small explanation of eliminating all infinity vectors

The first equation states that, if the multiplicity of the spec and code
model are both $\mathsf{once}$, then the problem is reduced to checking consistency of
models in which non-unique indexing is allowed, labelled with
$\mathsf{mult}$.

@@

>>>>

The first equation states that, if the multiplicity of the spec and code
model are both $\mathsf{once}$, then the problem is reduced to checking consistency of
models in which non-unique indexing is allowed, labelled with
$\mathsf{mult}$. Similarly, the second rule ensures that absence of
\texttt{readOnce} modifier in the specification does not prohibit a set of
unique stencil accesses from being consistent.

@@

One way implementation may deviate from the model is elimination of all $\infty$
offset vector that occurs when all indices are in non-neighbourhood form \eg{}
\mintinline{fortran}{b(42,0)}. The only generalisation scheme that can unify
with this pattern is the most general one, meaning it requires outright
rejection of an otherwise fine stencil computation. See the following example,
where not discarding all $\infty$ access pattern prevents verification:
%
\begin{minted}{fortran}
!= stencil forward(dim=1,depth=1) :: a
a(i) = a(i) + a(i+1) + a(1)
\end{minted}
